---
title: "Workshop 5"
author: "Yalan S4664845"
date: "10/03/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown workshop 5



```{r}
#install.packages("tidyverse")
library(tidyverse)
library(knitr)

dataset <- mpg
kable(dataset[1:15,],caption = "First 15 rows")

2.#Count the number of cars for each 'class' and their type of drive train 'drv'. Display the Top 5.

dataset %>%
  count(class)

dataset %>%
  count(class, drv, sort = TRUE) %>%
  top_n(5)

dataset %>%
  count(class, drv)

dataset %>%
  count(class, drv, sort = TRUE, name = "total cars") %>%
  top_n(5) %>%
  kable()

 top_5 <-dataset %>%
  count(class, drv, sort = TRUE, name = "totalcars") %>%
  top_n(5)
 
kable(top_5)

# have name of dataset on top ,we dont need to add dataset mane in ggploy or kable.
# if use ggplot or kable peparately, we have to ass dataset name


#3. Make a bar chart to show the number of cars per each type of drive train 'drv' in the top 5 'class' (by number of cars). Facet the chart for different type of drive train. Put title and custom legends.

ggplot(top_5, aes(class,totalcars)) +
  geom_col()

ggplot(top_5, aes(class,totalcars, fill=class)) +
  geom_col()+
  facet_wrap(~drv) +
  coord_flip()


ggplot(top_5, aes(class,totalcars,fill=class)) +
  geom_col()+
  facet_wrap(~drv) +
  coord_flip()+
  labs(x="class of cars", y="No of Cars", fill="class", title="top 5 class per type of drive train")

#4Create a dataset with new column for average city miles per gallon 'cty' for each 'class' of car for each 'manufacturer'. Show top 15 with highest average city miles per gallon.
#when use group with summarise always ungroup
new_avg_city_miles <-dataset %>%
  group_by(class,manufacturer) %>%
  summarise(avg_city_miles = mean(cty)) %>%
  ungroup()
#why summarise not mutate mutate create new variable. summirise only variables we needed.
new_avg_city_miles <-dataset %>%
  group_by(class,manufacturer) %>%
  summarise(avg_city_miles = mean(cty)) %>%
  ungroup() %>%
  arrange(desc(avg_city_miles))

kable(new_avg_city_miles[1:15,])


#5. Create a line graph to show all the 'manufacturer' with their average city miles per gallon for class 'compact'. Put title and custom legends.
#when create line graph 1. use geom_point together  geom_point 2.have to join point as a line group = 1
new_avg_city_miles%>%
  filter(class == "compact")  %>%
  ggplot(aes(manufacturer, avg_city_miles, group = 1))+
  geom_line() +
  geom_point()

# mutate is ask to reorger manufacturer
new_avg_city_miles%>%
  filter(class == "compact")  %>%
  mutate(manufacturer = fct_reorder(manufacturer, avg_city_miles)) %>% 
  ggplot(aes(manufacturer, avg_city_miles, group = 1))+
  geom_line() +
  geom_point() +
  labs(x="name of manufacturer", y="Average city miles per gallon", title = "average city miles for different manufacturer with compact")
